Supplementary Materials for CBEA: Competitive Balances for Taxonomic Enrichment Analysis

### 2022-02-17 cbea_revised.tex
Final final

\section*{Acknowledgments}
The authors thank Becky Lebeaux, Modupe Coker, Erika Dade, Jie Zhou, and Weston Viles for insightful comments and suggestions that greatly improved the paper. Funding for HRF provided by National Institutes of Health grants R21CA253408, P20GM130454 and P30CA023108. Funding for AGH provided by National Institutes of Health grant R01LM012723. Funding for QPN provide by National Institutes of Health grants K01LM012426,
R21CA253408, P20GM130454, and R01LM012723. The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

>>>>

\section*{Acknowledgments}
The authors thank Becky Lebeaux, Modupe Coker, Erika Dade, Jie Zhou, and Weston Viles for insightful comments and suggestions that greatly improved the paper.
